Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-19 notes.tex
completed the dimer consistency check part, it works !

			     &= \frac{2}{N}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]

@@

	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]\\

@@

\section{Analytic consistency checks}
\subsection{Single-particle Greens function and self energy for the Hubbard dimer}
The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \uparrow)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\). For $k=0$, we have
	\xi_{\vec k = 0} = e^{ikr} = 1
Substituting this into eq.~\ref{k_Gf} gives
	\label{Gk_dim}
	G(k=0,\uparrow) = \frac{2}{N}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]

@@

\section{Appendix: Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
\begin{equation}\begin{aligned}
	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = \pm t\ket{\pm}
\end{aligned}\end{equation}
In terms of these eigenstates, we can write
\begin{equation}\begin{aligned}
	c^\dagger_{0\uparrow}\ket{\text{GS}} 
	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
	&=x\ket{+} + y\ket{-}
\end{aligned}\end{equation}
where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other excitation, we can write
\begin{equation}\begin{aligned}
	c^\dagger_{1\uparrow}\ket{\text{GS}} 
	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
	&=x\ket{+} - y\ket{-}
\end{aligned}\end{equation}
Solving for $x$ and $y$ gives
\begin{equation}\begin{aligned}
	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
\end{aligned}\end{equation}

>>>>

			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]

@@

	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\

@@

\section{Analytic consistency checks}
\subsection{Single-particle Greens function and self energy for the Hubbard dimer}
The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \uparrow)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\). For $k=0$, we have
\begin{equation}\begin{aligned}
	\xi_{\vec k = 0} = e^{ikr} = 1
\end{aligned}\end{equation}
Substituting this into eq.~\ref{k_Gf} gives
\begin{equation}\begin{aligned}
	\label{Gk_dim}
	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
\end{aligned}\end{equation}
The expansion in terms of the exact eigenstates takes the form:
\begin{equation}\begin{aligned}
	c^\dagger_{0 \uparrow}\ket{\tilde 0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde 0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
	c_{0 \uparrow}\ket{\tilde 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde 0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
\end{aligned}\end{equation}
where $\ket{(3,1)\pm (\uparrow, \downarrow)}$ are the $N=(3,1), S^z = (+\frac{1}{2}, -\frac{1}{2})$ eigenstates of even $(+)$ and odd \((-)\) parity:
\begin{equation}\begin{aligned}
	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}\\
	H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
\end{aligned}\end{equation}
and \(x = \frac{a_2 - a_1}{2}, y = \frac{a_2 + a_1}{2}\). The orthogonal basis is therefore
\begin{equation}\begin{aligned}
	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}\\
	\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
\end{aligned}\end{equation}
The coefficients can thus be determined:
\begin{gather*}
	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde 0} = x, y\\
	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde 0} = x, -y\\
	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde 0} = y, x\\
	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde 0} = y, -x\\
	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t\\
	\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
\end{gather*}
We can see that $|C^0_-|^2 + {C^0_-}^* C^1_- = y^2 - y^2 = 0$ and $|\overline C^0_-|^2 + {\overline C^0_-}^* \overline C^1_- = x^2 - x^2 = 0$. So we do not need to consider those terms. With this preparation, we can now calculate the Greens function:
\begin{equation}\begin{aligned}
	G(k=0, \omega) = \left(|C^0_{+}|^2 + {C^0_{+}}^* C^1_{+} \right)\frac{1}{g_+} - \left(|\overline C^0_{+}|^2 + {C^0_{+}}^* \overline C^1_{+}\right)\frac{1}{\overline{g_+}} = \frac{2x^2}{\omega + E_{GS} - t} - \frac{2y^2}{-\omega + E_{GS} + t}
\end{aligned}\end{equation}
The final step is to recognize that $2x^2 = \frac{a_1^2 + a_2^2 -2a_1a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$, $2y^2 = \frac{a_1^2 + a_2^2 + 2a_1a_2}{2} = \frac{1}{2} + \frac{2t}{\Delta}$ and $E_{GS} = -\frac{\Delta}{2}$. Then,
\begin{equation}\begin{aligned}
	G(k=0, \omega) = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} - \frac{\frac{1}{2} + \frac{2t}{\Delta}}{-\omega - \frac{\Delta}{2} + t} = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}
\end{aligned}\end{equation}

@@

\section{Appendix: Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
\begin{equation}\begin{aligned}
	\ket{3\pm \uparrow} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{3\pm \uparrow} = \pm t\ket{3\pm \uparrow}
\end{aligned}\end{equation}
In terms of these eigenstates, we can write
\begin{equation}\begin{aligned}
	c^\dagger_{0\uparrow}\ket{\text{GS}} 
	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
	&=x\ket{3+ \uparrow} + y\ket{3- \uparrow}
\end{aligned}\end{equation}
where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other site excitation, we can write
\begin{equation}\begin{aligned}
	c^\dagger_{1\uparrow}\ket{\text{GS}} 
	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
	&=x\ket{3+ \uparrow} - y\ket{3- \uparrow}
\end{aligned}\end{equation}
Solving for $x$ and $y$ gives
\begin{equation}\begin{aligned}
	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
\end{aligned}\end{equation}
Similarly, we can also write the single-hole excitation $c_{0 \uparrow}\ket{GS}$ in terms of the $N=1, S^z = -\frac{1}{2}$ eigenstates, $\ket{1\pm \downarrow}$:
\begin{equation}\begin{aligned}
	\ket{1\pm \downarrow} = \frac{1}{\sqrt 2}\left(\ket{\downarrow, 0} \pm \ket{0, \downarrow}\right), && H^D \ket{1\pm \downarrow} = \mp t\ket{1\pm \downarrow}
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	c_{0 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{0, \downarrow} + a_2 \frac{1}{\sqrt 2}\ket{\downarrow, 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}\\
	c_{1 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{\downarrow, 0} + a_2 \frac{1}{\sqrt 2}\ket{0, \downarrow} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
\end{aligned}\end{equation}
